\documentclass[11pt,a4paper]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.85in, right=0.85in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{parskip}

% Color definitions
\definecolor{darkblue}{RGB}{0,51,102}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    urlcolor=darkblue,
    pdftitle={Cover Letter - Musthofa Joko Anggoro - StraitsX},
    pdfauthor={Musthofa Joko Anggoro}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

% ============================================================
% HEADER
% ============================================================
\begin{center}
    {\LARGE \textbf{MUSTHOFA JOKO ANGGORO}} \\[4pt]
    \small
    \faEnvelope\ \href{mailto:musthofaja.topa@gmail.com}{musthofaja.topa@gmail.com}
    \ $|$ \
    \faLinkedin\ \href{https://www.linkedin.com/in/musthofa-joko-anggoro/}{linkedin.com/in/musthofa-joko-anggoro}
    \ $|$ \
    \faGithub\ \href{https://github.com/topahilangharapan}{github.com/topahilangharapan}
    \ $|$ \
    \faGlobe\ \href{https://portfolio-topahilangharapan-personal.vercel.app/}{portfolio-topahilangharapan-personal.vercel.app}
\end{center}

\vspace{4pt}
\hrule
\vspace{14pt}

% ============================================================
% DATE & SALUTATION
% ============================================================
April 29, 2026

\vspace{6pt}
Hiring Team \\
StraitsX \\
Singapore

\vspace{6pt}
Dear StraitsX Hiring Team,

% ============================================================
% P1 — HOOK
% ============================================================
Reducing manual booking intervention by 85\% wasn't the original goal --- building an
automation pipeline that operators could actually trust was. That same instinct is what
draws me to StraitsX's AI Taskforce: the role isn't about using AI tools, it's about
designing the agentic workflows and internal infrastructure that make those tools
genuinely useful at scale.

% ============================================================
% P2 — PROOF
% ============================================================
At Traveloka, one of the largest flight inventory providers had no automated reschedule
path --- operators manually processed thousands of booking modifications daily. I built
an end-to-end pipeline with configurable scrapers, failover backup mechanisms, and 99.9\%
processing accuracy, cutting manual intervention by 85\%. The team stopped doing
repetition and started handling exceptions. Alongside that, I integrated GitHub Copilot
CLI into our development workflow to compress feedback loops and raise automated test
coverage --- the AI didn't write the features, but it meaningfully changed how fast we
could ship them safely.

% ============================================================
% P3 — FIT
% ============================================================
The part of this role I find most compelling is the MCP layer --- the connective tissue
between AI agents and internal systems. That's where the real adoption problems live: not
whether the model is capable, but whether it has the right context at the right time.
I've been exploring this both at work and outside it --- which is also how I ended up
building agent configuration and authoring workflows into my own portfolio. The
governance piece matters too: a system that can't be audited or safely constrained isn't
a productivity tool, it's a liability. That's a lesson I already applied when I built a
Credential Management System with AES-GCM encryption and granular audit logging at
Traveloka.

% ============================================================
% P4 — CTA
% ============================================================
I'd welcome the chance to talk through how StraitsX's Taskforce is thinking about the
boundary between agent capability and safety governance --- that's the design question I
find most interesting right now, and I suspect it's the hardest one on the team's
roadmap.

\vspace{10pt}
Sincerely,

\vspace{18pt}
\textbf{Musthofa Joko Anggoro}

% ============================================================
% FOOTER
% ============================================================
\vspace{10pt}
\hrule
\vspace{6pt}
\footnotesize
\textit{University of Indonesia, Fasilkom\ $\cdot$\ Information Systems\ $\cdot$\ GPA 3.84/4.00\ $\cdot$\ Expected graduation June--August 2026}

\end{document}
