\documentclass[11pt,a4paper]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.85in, right=0.85in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{fontawesome5}
\usepackage{parskip}

\definecolor{darkblue}{RGB}{0,51,102}
\hypersetup{colorlinks=true, urlcolor=darkblue,
    pdftitle={Cover Letter - Musthofa Joko Anggoro - Permata Bank},
    pdfauthor={Musthofa Joko Anggoro}}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{10pt}

\begin{document}

% ── HEADER ──────────────────────────────────────────────────
\begin{center}
    {\LARGE \textbf{MUSTHOFA JOKO ANGGORO}} \\[4pt]
    \small
    \faEnvelope\ \href{mailto:musthofaja.topa@gmail.com}{musthofaja.topa@gmail.com}
    \ $|$ \
    \faLinkedin\ \href{https://www.linkedin.com/in/musthofa-joko-anggoro/}{linkedin.com/in/musthofa-joko-anggoro}
    \ $|$ \
    \faGithub\ \href{https://github.com/topahilangharapan}{github.com/topahilangharapan}
    \ $|$ \
    \faGlobe\ \href{https://portfolio-topahilangharapan-personal.vercel.app/}{portfolio-topahilangharapan-personal.vercel.app}
\end{center}

\vspace{4pt}\hrule\vspace{14pt}

% ── DATE & SALUTATION ────────────────────────────────────────
April 30, 2026

\vspace{6pt}
Hiring Team \\
Permata Bank \\
Tangerang, Banten, Indonesia

\vspace{6pt}
Dear Permata Bank Hiring Team,

% ── P1 HOOK ──────────────────────────────────────────────────
Processing 1,000+ flight-booking modifications a day with 99.9\% accuracy sounds like
an automation win --- but the harder part was designing a core engine resilient enough
that \textbf{no transaction could silently fail}. That same design discipline is what drew me
to Permata Bank's Core Engine Developer role: a KBMI 3 bank running near-50 trillion
rupiahs in core capital demands exactly that level of stability from the systems underneath it.

% ── P2 PROOF ─────────────────────────────────────────────────
At Traveloka, one of Indonesia's largest flight inventory providers had no automated
reschedule path --- operators manually handled thousands of booking modifications daily.
I designed and built an end-to-end Java / Spring Boot engine with configurable scrapers,
failover logic, and structured audit logging, deployed on Linux production servers.
The result: \textbf{85\% reduction in manual intervention} at 99.9\% transaction accuracy.
Operators shifted from repetitive exception handling to genuine issue resolution --- the
kind of impact that only comes when the core engine underneath is solid.

% ── P3 FIT ───────────────────────────────────────────────────
Permata Bank's recognition in the HR Excellent Award 2024 for Learning Development tells
me this is a team that invests in engineers, not just headcount. That matters to me,
because I write code as a craft --- every design decision should be traceable and
defensible, not just functional. My background in Spring Boot microservices, PostgreSQL
(RDBMS) performance tuning, and CI/CD pipeline integrity maps directly to the core engine
work you've described, and I'm actively deepening my understanding of distributed
systems and high-availability architectures.

% ── P4 CTA ───────────────────────────────────────────────────
I'd welcome the chance to discuss how my work on transactional reliability at Traveloka
applies to Permata Bank's core engine challenges --- particularly around stability,
root-cause investigation, and failover design. I'm looking forward to exploring whether
this is the right match.

\vspace{10pt}
Sincerely,

\vspace{18pt}
\textbf{Musthofa Joko Anggoro}

% ── FOOTER ───────────────────────────────────────────────────
\vspace{10pt}\hrule\vspace{6pt}
\footnotesize
\textit{University of Indonesia, Fasilkom\ $\cdot$\ Information Systems\ $\cdot$\
GPA 3.84/4.00\ $\cdot$\ Expected graduation June--August 2026}

\end{document}
